---
title: "Marvel Trading Card"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    includes:
      in_header: "~/MarvelApp/MarvelCharacterSearch/header.html"
      after_body: "~/MarvelApp/MarvelCharacterSearch/footer.html"
params:
  set_author: "Stan Lee"
  n: NA
  s: NA
  l: NA
  comic_events: NA
author: "`r str_to_title(params$set_author, locale='en')`"
---
```{js, echo=FALSE}
$('.title').css('color', 'red')
```


```{css, echo=FALSE}
body {
  color: red;
  font-family: "Comic Sans MS", cursive, sans-serif;
}

.myClass {
  color: blue;
  font-family: "Arial Black", Gadget, sans-serif;
  font-size: 15px;
  
}
```

```{js, echo=FALSE}
$('.author').css('color', 'gold')
```


```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
library(stringr)
```

<hr>

<center><h2>Biography: "`r str_to_title(params$set_author, locale='en')`"</h2></center>

<hr>


<blockquote class="myClass">

"`r params$l`"

</blockquote>


<center><h2>"`r str_to_title(params$set_author, locale='en')`"</h2></center>

<center>
```{r echo=FALSE, fig.cap= str_to_title(params$set_author), out.width = '400px',out.height="400px"}

image <- params$s

knitr::include_graphics(image,auto_pdf = TRUE)

```
</center>

<hr>

<center><h2>Series `r str_to_title(params$set_author, locale='en')` is part of:</h2></center>

<hr>


<div class="container">
<div class="row">
<div class="col-sm-4">
<h4>`r params$comic_events$title_one`</h4>
<img id="myImage"  src="`r params$comic_events$one`" height="300" width="300">
<blockquote class="myClass">

"`r params$comic_events$descrip_one`"

</blockquote>
</div>
<div class="col-sm-4">
<h4>`r params$comic_events$title_two`</h4>
<img id="myImage"  src="`r params$comic_events$two`" height="300" width="300">
<blockquote class="myClass">

"`r params$comic_events$descrip_two`"

</blockquote>
</div>
<div class="col-sm-4">
<h4>`r params$comic_events$title_three`</h4>
<img id="myImage"  src="`r params$comic_events$three`" height="300" width="300">
<blockquote class="myClass">

"`r params$comic_events$descrip_three`"

</blockquote>
</div>
<div class="col-sm-4">
<h4>`r params$comic_events$title_four`</h4>
<img id="myImage"  src="`r params$comic_events$four`" height="300" width="300">
<blockquote class="myClass">

"`r params$comic_events$descrip_four`"

</blockquote>
</div>
<div class="col-sm-4">
<h4>`r params$comic_events$title_five`</h4>
<img id="myImage"  src="`r params$comic_events$five`" height="300" width="300">
<blockquote class="myClass">

"`r params$comic_events$descrip_five`"

</blockquote>
</div>
<div class="col-sm-4">
<h4>`r params$comic_events$title_six`</h4>
<img id="myImage"  src="`r params$comic_events$six`" height="300" width="300">
<blockquote class="myClass">

"`r params$comic_events$descrip_six`"

</blockquote>
</div>
</div>
</div>